---
title: "Problem Set 3"
author: "Westley Cook"
date: "2/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(reprex)
library(janitor)
library(gt)

```

```{r read_in_data, include=FALSE}

xian <- read_csv("./raw-data/xian_data.csv",
                 skip = 3,
                 na = "undefined") %>% 
  clean_names()
  

# Used glimpse() and summary() to look at the data


```

## Madlibs

```{r mad-lib-1, include=FALSE}

treatment_respondents <- xian %>% 
  filter(treatment == 1) %>% 
  count() %>% 
  pull(n)

```

1. **`r treatment_respondents`** respondents are in the treatment group.

```{r mad-lib-2, include=FALSE}

xian %>% 
  group_by(treatment) %>% 
  summarize(govt_overall_avg_by_group = mean(eval_gov_overall))

xian %>% 
  filter(treatment == 1) %>% 
  summarize(govt_avg_in_treatment_group = mean(eval_gov_overall))



```


2. Among respondents from the treatment group, the government has an average **X**
rating.

```{r mad-lib-3, include=FALSE}

most_common_traffic <- xian %>% 
  count(eval_gov_traffic) %>% 
  arrange(desc(n)) %>% 
  slice(1) %>% 
  pull(eval_gov_traffic)

```


3. The most common rating for the government’s handling of traffic is **`r most_common_traffic`**.

```{r mad-lib-4, include=FALSE}



```


4. **X** respondents have given the government a 10 rating overall or on demolitions
or on traffic.

5. But only **X** gave the government a 10 rating overall and on demolitions and on
traffic.

The variable ‘news_source’ asks respondents to list which news sources they get
their news from. Some respondents answered more than one option, so their answer
lists a number of letters together. A means “Television”, B means “Newspapers”,
C means “Radio”, etc

6. The number of respondents who get their news from Television is **X**

7. Of the 4 different locations where the respondents were surveyed, the
following two locations end with “square”: **X,X**
