---
title: "Problem Set 3"
author: "Westley Cook"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Loading libraries that I assume will come in handy: tidyverse for its dplyr
# and ggplot2 packages, reprex in case I need to use it to ask for help online,
# janitor to clean my data, and gt because I'll have to produce a table.

library(tidyverse)
library(reprex)
library(janitor)
library(gt)

```

```{r read_in_data, include=FALSE}

# This r chunk reads in the xian data and cleans it.

xian <- read_csv("./raw-data/xian_data.csv",
                 
# Skipping three rows to get the column names to the top of the data frame
                 
                 skip = 3,

# Setting all the "undefined" values to NA

                 na = "undefined") %>% 
  
# Cleaning column names to make them easier to use
  
  clean_names()

# As I worked through the specifics of the commands and arguments I'd use to
# read in the data, I used glimpse() and summary() commands to  to look at the
# data (e.g. so I'd know how many rows to skip).


```

## Madlibs

```{r mad-lib-1, include=FALSE}

# This r chunk assigns an object to use in mad lib 1.

# Filtering xian data for only those rows where treatment is 1 (meaning those
# respondents who received treatment), then counting the number of rows and
# pulling the value of n and assigning it to the object treatment_respondents

treatment_respondents <- xian %>% 
  filter(treatment == 1) %>% 
  count() %>% 
  pull(n)

```

1. **`r treatment_respondents`** respondents are in the treatment group.

```{r mad-lib-2, include=FALSE}

# This r chunk assigns an object to use in mad lib 2.

# As above, filtering xian for those rows where treatment is 1;, then creating a
# column (gov_avg_in_treatment_group) to house the average of overall ratings
# for members of the treatment group, removing all the NA values because they're
# incompatible with the mean() operation. Pulling the result and assigning it to
# the object gov_avg_rating_in_treatment_group (which is probably too long a
# name, but it's descriptive).

gov_avg_rating_in_treatment_group <- xian %>% 
  filter(treatment == 1) %>% 
  summarize(gov_avg_in_treatment_group = mean(eval_gov_overall, 
                                              na.rm = TRUE)
            ) %>% 
  pull(gov_avg_in_treatment_group)

```

2. Among respondents from the treatment group, the government has an average
**`r gov_avg_rating_in_treatment_group`** rating.

```{r mad-lib-3, include=FALSE}

# This r chunk assigns an object to use in mad lib 3.

# To find the most common rating for traffic, I count() the eval_gov_traffic
# column (which gives me two columns as a result, one for the values that make
# an appearance in the eval_gov_traffic column and one called n which shows how
# many times they appear). I then arrange the dataframe in descending order (so
# the most commonly-given rating is in the first row) and slice() that row. I
# pull() the value in the eval_gov_traffic column and assign it to
# most_common_traffic.

most_common_traffic <- xian %>% 
  count(eval_gov_traffic) %>% 
  arrange(desc(n)) %>% 
  slice(1) %>% 
  pull(eval_gov_traffic)

```

3. The most common rating for the government’s handling of traffic is 
**`r most_common_traffic`**.

```{r mad-lib-4, include=FALSE}

# This r chunk assigns an object to use in mad lib 4.

# I use filter() to leave only the rows in the dataframe where either overall,
# demolitions, or traffic rating is 10. I then count() those rows and pull() the
# n column to assign the total count (number of times a row in the dataframe
# contains 10 in any of the three rating categories) to any_ten_count.

any_ten_count <- xian %>% 
  filter(eval_gov_overall == 10 |
         eval_gov_demo == 10 |
         eval_gov_traffic == 10) %>% 
  count() %>% 
  pull(n)

```

4. **`r any_ten_count`** respondents have given the government a 10 rating
overall or on demolitions or on traffic.

```{r mad-lib-5, include=FALSE}

# This r chunk assigns an object to use in mad lib 5.

# I modify the code from mad lib 4 just slightly, replacing "or" bars (|) with
# commas in the filter function so it will leave me only with those rows in the
# dataframe in which ALL ratings were 10.

all_tens <- xian %>% 
  filter(eval_gov_overall == 10,
         eval_gov_demo == 10,
         eval_gov_traffic == 10) %>% 
  count() %>% 
  pull(n)

```

5. But only **`r all_tens`** gave the government a 10 rating overall and on
demolitions and on traffic.

```{r mad-lib-6, include=FALSE}

# This r chunk assigns an object to use in mad lib 6.

# Similar process to that in mad lib 5, but instead of filtering for just the
# value "A" (which would leave me with those respondents who ONLY get their news
# from Television and exclude those who get news from Television and other
# sources) I filter() for any value in the news_source column which contains the
# letter "A" using str_detect().

tv_respondents <- xian %>% 
  filter(str_detect(news_source, 
                    "A")
         ) %>% 
  count() %>% 
  pull(n)

```

6. The number of respondents who get their news from Television is 
**`r tv_respondents`**.

```{r mad-lib-7, include=FALSE}

# This r chunk assigns an object to use in mad lib 7.

# As in mad lib 6, I use str_detect() to filter() for values in the location
# column which contain "square". After running that command and looking at the
# resulting table, I see that rows 1 and 4 are the first rows in the dataframe
# to contain their respective values, so I slice() those rows and pull() the
# values, assigning them to square_locations.

square_locations <- xian %>% 
  filter(str_detect(location, 
                    "square")
         ) %>% 
  slice(1, 4) %>% 
  pull(location)

```

7. Of the 4 different locations where the respondents were surveyed, the
following two locations end with “square”: **`r square_locations`**.

## Data Wrangling

**1.a**

```{r table-untidy, echo=FALSE}

# This r chunk first creates a new subset of the xian data with the columns
# requested by the assignment, then uses that subset to produce a neat (but
# untidy) table.

# Creating a subset of xian data, selecting the columns I want in the order in
# which I want them to appear in my table.

xian_subset_untidy <- xian %>% 
  select(respondent, 
         eval_gov_overall, 
         eval_gov_traffic, 
         eval_gov_demo)

# Now making the table itself.

xian_subset_untidy %>% 
  
# Slicing the first ten rows because the assignment asks for the first ten
# respondents (and in this dataframe, one respondent is on each row).
  
  slice(1:10) %>% 
  
# Putting the table in a neat format
  
  gt() %>% 
  
# Adding header
  
  tab_header(title = "Untidy Data") %>% 
  
# Creating a spanner column label for overall, traffic, and demolitions columns.
  
  tab_spanner(label = "Evaluations of Government Performance",
              columns = vars(eval_gov_overall, 
                             eval_gov_traffic, 
                             eval_gov_demo)
              ) %>%
  
# Changing the column labels to make them pretty.
  
  cols_label(eval_gov_overall = "Overall",
             eval_gov_traffic = "Traffic",
             eval_gov_demo = "Demolitions",
             respondent = "Respondent Number")

```

**1.b**

```{r table-tidy, echo=FALSE}

# This r chunk takes the untidy subset from part 1.a and uses pivot_longer() to
# make it tidy before using gt() and a few other modifying commands to grab the
# first 10 respondents (NOT the first 10 rows anymore) and make the table
# pretty.

xian_subset_untidy %>% 
  
# Taking the three separate evaluation columns and making from them two new
# columns: the names of the old columns will fall under one column ("type") and
# the values in them will fall under another ("rating").
  
  pivot_longer(cols = c(eval_gov_overall, 
                        eval_gov_traffic,
                        eval_gov_demo),
               names_to = "type",
               values_to = "rating") %>% 
  
# To get the first ten respondents, filtering this time by respondent less than
# or equal to 10; can't just slice() the first ten rows this time, because each
# respondent takes up three rows.
  
  filter(respondent <= 10) %>% 
  
# Changing the values in the "type" column to a prettier-to-display version of
# themselves so they'll show up nicely in my table.
  
  mutate(type = recode(type, 
                       eval_gov_overall = "Overall",
                       eval_gov_traffic = "Traffic",
                       eval_gov_demo = "Demo")
         ) %>% 
  
# Making the table look nice  
  
  gt() %>% 
  
# Adding title
  
  tab_header(title = "Tidy Data") %>% 
  
# Changing column labels
  
  cols_label(respondent = "Respondent Number",
             type = "Type of Evaluation",
             rating = "Performance Rating")

```

**2.** 

```{r table-potential-outcomes, echo=FALSE}

# This r chunk creates a new potential outcomes table from the xian data.

# Selecting from xian the columns I'll need for the table in the order in which
# I want them to appear.

xian %>% 
  select(respondent,
         treatment,
         control,
         eval_gov_overall) %>% 
  
# Creating new column (eval_under_treatment) which will copy its values from
# eval_gov_overall in rows where treatment is 1, and insert "?" for its values
# in rows where treatment is NOT 1. Doing this before mutating the existing
# eval_gov_overall column for two reasons: 1) I don't want to accidentally lose
# any values, 2) I want this column on the far right side of the table.
  
  mutate(eval_under_treatment = ifelse(treatment == 1,
                                       eval_gov_overall,
                                       "?")
         ) %>% 
  
# Renaming the eval_gov_overall in preparation to modify its values to only
# include those from the control group respondents.
  
  rename(eval_under_control = eval_gov_overall) %>% 
  
# Mutating the eval_under_control column in a similar way as I did with the
# eval_under_treatment column, such that when treatment is 0 it keeps the values
# already there, but if treatment is NOT 0 it replaces those values with "?".

# Note that in both mutated columns, NA values will still show up as they are;
# this might look odd on the table, but I think it's an honest way of displaying
# the data. Leaving the NA values at least seems better than the two
# alternatives I thought of: replacing NA with "?" (which would leave the reader
# confused about why outcomes under treatment and control were BOTH unknown and
# might look like a mistake), or cutting that row out of the table (which would
# leave the attentive reader confused about why respondent 4 was missing, and
# might also seem like a mistake).
  
  mutate(eval_under_control = ifelse(treatment == 0,
                                     eval_under_control,
                                     "?")
         ) %>% 
  
# Taking the first ten rows of the dataframe (which, here, is the first ten
# respondents) and putting them into a nice-looking table.
  
  slice(1:10) %>% 
  gt() %>% 
  
# Adding title  
  
  tab_header(title = "Potential Outcomes") %>% 
  
# Adding spanner label for columns eval_under_control and eval_under_treatment  
  
  tab_spanner(label = "Potential Outcomes",
              columns = vars(eval_under_control,
                             eval_under_treatment)
              ) %>% 
  
# Adding footnote as shown in the table I'm replicating; had to specify "title"
# within cells_title() to get a warning message to disappear.
  
  tab_footnote(footnote = "Treatment is a 2 minute video about Chinese sports 
                           performance",
               locations = cells_title("title")
               ) %>% 
  
# Giving the columns pretty labels  
  
  cols_label(respondent = "Respondent",
             treatment = "Treatment",
             control = "Control",
             eval_under_control = "Under Control",
             eval_under_treatment = "Under Treatment") %>% 
  
# Center-aligning the values in each column  
  
  cols_align(align = "center")

```

**3.**

```{r demographics-setup, include=FALSE}

# This r chunk loads the demographics data (downloaded from canvas and placed in
# r-data/, a subdirectory of this project) and joins that data to the xian data
# by matching the "respondent" values from each dataframe.

# It is in its own chunk so I can use include=FALSE to make sure it won't show
# up in the knitted html document.

load("r-data/demographics.Rdata")

xian_demographics <- xian %>% 
  inner_join(demographics, by = "respondent")

```

```{r table-demographics, echo=FALSE}

# This r chunk creates a nice table to show demographic information for the
# treated individuals who gave the highest evaluations of the government's
# performance on traffic.

# Filtering the newly-joined xian_demographics dataframe for only the treated
# population.

xian_demographics %>% 
  filter(treatment == 1) %>%
  
# Selecting the variables I want in the order in which I want them to appear in
# the table; mimicking the layout of table I'm replicating.
  
  select(respondent, eval_gov_traffic, age, gender) %>% 
  
# Sorting the data with the highest evaluations at the top and slicing the first
# five rows, again mimicking the layout of the table I'm replicating.
  
  arrange(desc(eval_gov_traffic)) %>%
  slice(1:5) %>% 
  
# Making a nice table  
  
  gt() %>% 
  
# Adding title and subtitle; text copied from table I'm replicating.
  
  tab_header(title = "Highest Evaluators of Government Performance on Traffic:",
             subtitle = "Among Treated Individuals") %>% 
  
# Adding footnote; text copied from table I'm replicating. Specified location as
# "title" within cells_title() to make a warning message disappear.
  
  tab_footnote(footnote = "Evaluation on Scale from 1 to 10",
               location = cells_title("title")) %>% 
  
# Labelling the columns with pretty names to complete the display; text again
# copied from the table I'm replicating.
  
  cols_label(respondent = "Respondent",
             eval_gov_traffic = "Evaluate Government Performance",
             age = "Age",
             gender = "Gender")

```

**4.**

```{r scatterplot-setup, include=FALSE}

# This r chunk prepares the dataframe to be plotted (plotting itself happens in
# the next r chunk). It's in its own r chunk so I can use include=FALSE to keep
# it out of the finished html document.

# Taking the xian_demographics dataframe and changing the treatment variable to
# a factor instead of a numeric (which is necessary to get the color to show
# properly on the plot when I map treatment onto color).

eval_by_treatment_education <- xian_demographics %>% 
  mutate(treatment = as.factor(treatment)) %>%
  
# Omitting NA values because it was giving me a warning about implicit NA in the
# education column
  
  na.omit() %>% 
  
# Grouping by education and treatment, then taking the mean of eval_gov_overall
# and assigning it to a new variable (avg_eval).
  
  group_by(education, treatment) %>%
  summarize(avg_eval = mean(eval_gov_overall))

```

```{r replicate-scatterplot, echo=FALSE}

# This r chunk creates a scatterplot using the newly-created
# eval_by_treatment_education dataframe.

# Plotting education on the x axis (reordering the factors to replicate the
# ordering of the model plot, which is good because it puts level of education
# from least to greatest) and avg_eval on the y axis, with treatment mapped to
# color.

eval_by_treatment_education %>% 
  ggplot(aes(x =  fct_relevel(education,
                              "Primary",
                              "Incomplete secondary",
                              "Complete secondary",
                              "Some university",
                              "University completed"),
             y = avg_eval,
             color = treatment)
         ) +
  
# Making it a scatterplot  
  
  geom_point() +
  
# Giving the plot a title. The text for the plot title is long, and thus
# unfortunately goes over the 80-character-per-line style guide limit. I used \n
# to insert both of the line breaks necessary to match the formatting of the
# model plot, because the formatting got wonky if I used actual line breaks in
# the .Rmd file. I wasn't sure how to replicate the plot formatting exactly
# without having this one small style guide violation.
  
  labs(title = "Government Performance Evaluations \n By Treatment Group \n and Education Level",
 
# Labeling the x axis and y axis, copying the label text from the model plot.
 
       x = "Education",
       y = "Average Evaluation") +
  
# Getting rid of the gray/tan background
  
  theme_bw() +
  
# Making other formatting adjustments: getting rid of the background grid,
# moving the legend to the top, getting rid of the full border around the plot
# and replacing it with just the left and bottom axes, rotating the text on the
# x axis to match the format of the model plot.
  
  theme(panel.grid = element_blank(),
        legend.position = "top",
        panel.border = element_blank(),
        axis.line.x.bottom = element_line(),
        axis.line.y.left = element_line(),
        axis.text.x = element_text(angle = 45,
                                   hjust = 1)
        ) +
  
# Giving the legend a proper label.  
  
  scale_color_discrete(name = "Viewed Sports Video")

```

**5.**

```{r gold-medal-setup, include=FALSE}

# This r chunk scrapes data from wikipedia to use in the olympic medal table.
# It's in a separate chunk from the plot so I can hide it using include=FALSE.

# Loading the rvest package to use for data scraping.

library(rvest)

# Reading the html into an object (olympics_html)

olympics_html <- read_html("https://en.wikipedia.org/wiki/2008_Summer_Olympics")

# Scraping the necessary table from the html document. 

olympic_table <- olympics_html %>% 
  
# Grabbing the "table" nodes to see 
  
  html_nodes(css = "table") %>% 
  
# After seeing the output of different tables in the html doc, identified number
# 8 as the one I wanted and selected it
  
  .[8] %>% 
  
# Importing the table itself as a table into R
  
  html_table()

# Turning the table into a dataframe

olympic_df <- olympic_table %>% 
  as.data.frame()

```

```{r replicate-gold-medal-chart, echo=FALSE}

# This r chunk plots the olympic medal dataframe from above, replicating as
# nearly as possible the model plot.

# Slicing the first ten rows of olympic_df to get rid of the row with totals
# (which isn't necessary for the plot).

olympic_df %>% 
  slice(1:10) %>% 
  
# Plotting number of gold medals on the y axis and country on the x axis,
# ordering the x axis factors by quantity of gold medals earned (in descending
# order, with the country with the most medals on the left).
    
  ggplot(aes(x = fct_reorder(Nation,
                             Gold,
                             .desc = TRUE),
             y = Gold)) +
  
# Making it a bar plot with bars separated  
  
  geom_col() + 
  
# Adding title for plot and labels for x and y axis, using different functions
# than those used above because I wanted to test new functions to make sure I
# could use them properly.
  
  ggtitle("Number of Gold Medals in 2008 Beijing Olympics") +
  xlab("Country") +
  ylab("Gold Medals") +
  
# Getting rid of the gray/tan background  
  
  theme_bw() +

# Making finishing-touch formatting adjustments: removing the border from the
# plot and replacing it with just the x and y axis lines, and removing the panel
# grid.
  
  theme(panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.line.x.bottom = element_line(),
        axis.line.y.left = element_line()
        )

```

##### Worked With:
Brian Kim
